### 2017-10-29 paper.tex
Final formatting

\textbf{Fig 1. Graphical abstract of ten simple rules for collaborative lesson development.} \textbf{1.} To clarify your audience, consider writing learner profiles (see Box 1). \textbf{2.} Make lessons modular by breaking them into small, single-purpose modules. \textbf{3.} Teach your instructors the best practices for developing, delivering, and maintaining lessons. \textbf{4.} Encourage and empower contributors by making the contribution process transparent and straightforward. \textbf{5} Build a community around lessons by creating opportunities for participation and mentorship. \textbf{6.} Publish new version periodically and recognize contributors by their unique identifiers (e.g., ORCID). \textbf{7.} Evaluate lessons during and after class for a complete picture of the lessons' efficacy. \textbf{8.} Reduce, re-use, or recycle lessons before creating a new one from scratch. \textbf{9.} Link to other resources that complement the lesson content. \textbf{10.} Remember that you can't please everyone in your audience or community.

\textbf{Fig 2. Collaborative open lesson development.} Following the decision to develop 
lessons, activities focus on lesson development as well as community building. 
Boxes surrounded by dotten lines represent community contributions to lessons.
Dashed arrows represent connections to activities outside the original lesson design.
The box enclosed in a dash-dotted line represents unaffiliated learning resources.

@@

An example of how to teach such pedagogical practices
is Software Carpentry's (\url{https://software-carpentry.org/}) instructor training program.
First offered in 2012,
it is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
In addition to a focus on pedagogy,
the course introduces everyone who takes it to who Software Carpentry's lessons are for,
how they are delivered,
and how they are maintained.
Largely as a result of this training,
several hundred people per year now contribute to Software Carpentry's lessons.

@@

>>>>

\begin{mdframed}
\noindent
\textbf{Fig 1. Graphical abstract of ten simple rules for collaborative lesson development.} \textbf{1.} To clarify your audience, consider writing learner profiles (see Box 1). \textbf{2.} Make lessons modular by breaking them into small, single-purpose modules. \textbf{3.} Teach your instructors the best practices for developing, delivering, and maintaining lessons. \textbf{4.} Encourage and empower contributors by making the contribution process transparent and straightforward. \textbf{5} Build a community around lessons by creating opportunities for participation and mentorship. \textbf{6.} Publish new version periodically and recognize contributors by their unique identifiers (e.g., ORCID). \textbf{7.} Evaluate lessons during and after class for a complete picture of the lessons' efficacy. \textbf{8.} Reduce, re-use, or recycle lessons before creating a new one from scratch. \textbf{9.} Link to other resources that complement the lesson content. \textbf{10.} Remember that you can't please everyone in your audience or community.
\end{mdframed}

\begin{mdframed}
\noindent
\textbf{Fig 2. Collaborative open lesson development.} Following the decision to develop 
lessons, activities focus on lesson development as well as community building. 
Boxes surrounded by dotten lines represent community contributions to lessons.
Dashed arrows represent connections to activities outside the original lesson design.
The box enclosed in a dash-dotted line represents unaffiliated learning resources.
\end{mdframed}

@@

An example of how to teach such pedagogical practices
is Software Carpentry's instructor training program.
First offered in 2012,
it is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
In addition to a focus on pedagogy,
the course introduces everyone who takes it to who Software Carpentry's lessons are for,
how they are delivered,
and how they are maintained.
Largely as a result of this training,
several hundred people per year now contribute to Software Carpentry's lessons.

@@

In 2015,
Software Carpentry established a Mentoring Subcommittee to support instructors
as they progress through training, teaching, curriculum development.
The Mentoring Subcommittee has promoted community building
by providing virtual spaces where instructors from all over the world can share success stories
and discuss strategies for overcoming challenges.
This has helped strengthen the community and provided insight into how lessons can be improved
(\ruleref{evaluate}).
